RNeXML: Parsing and Serializing the Next Generation of Phyloinformatic Data in R

### 2014-02-20 inst/doc/manuscript.Rmd

* Why NeXML -- because Nexus standard isn't a standard.  Developers extend it arbitrarily to meet their needs, making it incompatible.  Cannot represent horizontal gene transfer, ambiguous use of symbols, cannot be extended reliably, no validator.  NeXML solves all of these problems [Vos _et al._ 2012] with a state-of-the-art data management format.

@@

@@

This project was supported in part by a grant from the Alfred P Sloan Foundation (CB and KR), NSF Grant DBI-1306697 (CB), ... `RNeXML` is part of the rOpenSci project, [http://ropensci.org].

>>>>

* Why NeXML -- because Nexus standard isn't a standard.  Developers extend it arbitrarily to meet their needs, making it incompatible.  Cannot represent horizontal gene transfer, ambiguous use of symbols, cannot be extended reliably, no validator.  NeXML addresses all of these problems [Vos _et al._ 2012] with a state-of-the-art data management format.

@@

### Taxonomic identifiers

Add taxonomic identifier metadata to the OTU elements:

```{r}
nex <- add_trees(bird.orders)
nex <- nexml_taxize(nex)
```

@@

This project was supported in part by a grant from the Alfred P Sloan
Foundation (CB and SC), NSF Grant DBI-1306697 (CB), ... `RNeXML` is part
of the rOpenSci project, [http://ropensci.org].
